What We Eval in the Shadows

### 2021-08-11 paper/main.tex
Fix

The use of \eval with \code{substitute} is a general pattern that we often see
in R packages. It is used to make the interfaces more flexible. For example the
\c{subset}, which selects columns in a data frame, uses it to allow to specify
the selected columns using either the column name or index. For example
\c{subset(df, sel=c(1,B,x))} returns a subset of \code{df} with the first
column, the column named \code{B} and whatever column is at index the variable
\code{x} holds.

>>>>

The use of \eval with \code{substitute} is a general pattern that we often see
in R packages. It is used to make the interfaces more flexible. For example the
\code{subset}, which selects columns in a data frame, uses it to allow to specify
the selected columns using either the column name or index. For example
\code{subset(df, sel=c(1,B,x))} returns a subset of \code{df} with the first
column, the column named \code{B} and whatever column is at index the variable
\code{x} holds.
